The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-17 paper/Analisis.tex
A couple of paragraphs in discussion section

We start by a quantitative discussion of the line morphology. Here we
follow  following a classification of $Ly\alpha$ profiles made by
\cite{Kulas12}. They presented observational results for star forming
galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
They classified the observed lines into four groups. In Group I the
red peak is stronger that in the blue, in Group II the blue peak is
stronger, in Group III there are single peaked profiles while while
Group IV containes multipeaked lines.

Neither Group I nor II can be explained by rotation. However, the
morphologies of the lines in Group III and IV are similar to some of
the results obtained in this paper.

Group III profiles are better represented by galaxies rotating at $V >
100 kms^{-1}$\\

Comparing with the sample of (Kulas et al) we observe that rotational effects could be 
associated in group IV and V in galaxies where the difference between the two peaks is 
small and .

No effects asociated with inflows or outflows

... The results derived in this paper have consequences on the
interpretation of galaxy observations in the Lyman alpha line.

..compare steidel et al (2011)

% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail
% observaciones, Kulas, YAMADA  off-center emission

@@

\section*{Appendix A: Tables}

>>>>

We start by a quantitative discussion of the line morphology. Here we
follow a classification of $Ly\alpha$ profiles made by
\cite{Kulas12}. They presented observational results for star forming
galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
They classified the observed lines into four groups. In Group I the
red peak is stronger than the blue, For our porpoises Group II and Group II
with the blue peak stronger are the same, Group IV contains double-peak
profiles with roughly the same flux and finally group IV present multi-peaked 
lines.

Neither Group I nor II  and III can be fully explained by rotation. However,
 some comments about some of the galaxies in this groups must be done, in 
 particular for those galaxies in which the flux in between the two peaks is
 high rotation must be present due to the fact this is until now the most 
 efficient mechanism which produces this effect.

The same argument explained above applies to group IV in which the flux
in between of the two peaks is high ( $ \geq 70 \%$ of the highest peak), 
concerning group V in which multiple-peaks appear homogeneous and central
models can not reproduce such a profiles. While the off-center model could 
generate similar profiles which is the case of (put reference when the fig.
is ready) when tree peaks could appear but with roughly the same flux, this
multiple-peaks still need a better comprehension of the gas kinematics.

An other interesting sample of LAEs was presented by \cite{Yamada2012} 
for 91 LAEs at $z=3.1$. From that sample 31 LAEs ($\sim 33 \%$) present 
a single peak profile, if this single peak is present an asymmetry it 
can be explained with the outflow model \cite{Verhamme2008} due to the fact that 
we don't find any asymmetry due to rotation in  both homogeneous and central
models, while in the off-center model ---. But if it is not the 
case (put LAEs name for those that do not present asymmetry) now they can
be understanding with rotation.

Even in profiles where the double-peaked is presented rotation also could 
be present as it is seen in Fig.\ref{fig:differentvelocities} where rotation
makes that the central part of the line is higher than in profiles where 
there is no rotation. This could be the case of 13 LAEs in the sample of 
\cite{Kulas12} where there is a double-peak profile with similar heigh and 
a central notorious part.

Until now when single peaked profiles are present we associate this to
the presence of inflows and outflows due to the asymmetry of the line
, but in the case in which the profile have symmetry we could say that
rotation in the principal effect governing the galaxy. For this reason 
a detailed study involving inflows/outflows and rotation kinematics would 
give as better understanding of the $\mathrm{Ly} \alpha$ profiles we 
measured.

% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail
% observaciones, Kulas, YAMADA  off-center emission 
% See steidel et al (2011) findings.

@@
